
Remove Objects from Environment
```{r}
ls()
rm(list = ls())
```

```{r}
suppressMessages(library(rvest))
suppressMessages(library(tidyverse))
suppressMessages(library(magrittr))
suppressMessages(library(scales))
suppressMessages(library(knitr))
suppressMessages(library(lubridate))
suppressMessages(library(plyr))
suppressMessages(library(dplyr))
suppressMessages(library(xml2))
suppressMessages(library(rvest))
```

Load RDS file that contains the list of artist that we need:
```{r}
canada<-readRDS(file = "spotify_CA.rds")
usa<-readRDS(file = "spotify_USA.rds")
artist.info<-rbind(usa,canada)
artist.info<-artist.info[,3]
artist.info<-data_frame(unique(artist.info))
names(artist.info) <- c("Artist")
head(artist.info)
```


```{r}

```

Artist without a Wikipedia link:
Sheck Wes
benny blanco
Lil Mosey
Flipp Dinero
Bryce Vine
Silk City
Dean Lewis
Nio Garcia
Social House
Lil Skies
Rich The Kid
Famous Dex
YNW Melly
YBN Nahmir
Smokepurpp
Loud Luxury
Dynoro
Ava Max
NAV
Gryffin
Gunna
Normani
Vice
Bob"Boris" Pickett & The Crypt-Kickers
The Citizens of Halloween
Bob"Boris" Pickett
Carly Rae Jepsen
Moneybagg Yo
Mitchell Tenpenny
K/DA
Comethazine
Kris Kross Amsterdam
GASHI
Pressa
The City of Prague Philharmonic Orchestra
Offset
J.I.D
KILLY

```{r}

lyrics<- c()## which is actually for location
dfALL<- data.frame()
for(i in seq_along(artist.info$Artist)) {
  tryCatch({
        #we are pulling the row from the main file artist.info$Artist i.e. "Post Malone"
        for_url_name <- artist.info$Artist[i]#"Post Malone" #artist.info$Artist[i]
        #we are eliminating spaces and making lower case each row i.e. "Post_Malone"
        for_url_name <- str_replace_all(for_url_name,"\\s+","-")
        ## create url i.e. [1] "http://lyrics.wikia.com/wiki/Post_Malone"
        paste_url <- paste0("https://www.ticketcity.com/concerts/", for_url_name,"-tickets.html")
        ## we are hitting the website and getting the data that we need = this out put looks messy
        
        for_html_code <- read_html(paste_url)
        for_lyrics <- html_nodes(for_html_code,".location")
        test1<-html_text(for_lyrics)

        for_html_code <- read_html(paste_url)
        for_lyrics <- html_nodes(for_html_code,".date")
        test2<-html_text(for_lyrics)
        
        leng<-length(test2)
        test3<- c()
        name<-artist.info$Artist[i]
        
        for (i in (1:leng)) {
           test3[i]<-  name
        }
        
        if(length(test1)==length(test3)){        
          df=data.frame(test3,test2,test1)
        }
        dfALL<- rbind(df,  dfALL)
  }, error=function(e){})
}
View(dfALL)
## optional: add in 3 second delay to avoid IP block
#Sys.sleep(2)

```


```{r}
# Saving object to a file.
saveRDS(dfALL, file = "concerts.rds")
# Write CSV in R
write.csv(dfALL, file = "concerts.csv")
```
